\section{Introduction}

\input{RASD/Section1/purpose.tex}
\input{RASD/Section1/scope.tex}

\subsection{Definitions, Acronyms, Abbreviations}
    %questa sezione DEVE essere aggiornata durante la definizione del documento.
    This section contains the definitions for people that may not know what a specific concept is, acronyms and abbreviations used throughout the document.

    \subsubsection{Definitions}
    \begin{itemize}
        %dobbiamo inserire qualche altra definizione?
        \item \textbf{Bike Path:} a route deemed suitable for cycling. This includes paths with a proper bike track or roads where cars are rare and speed limits are 
        compatible with the average speed of a bike.
        \item \textbf{Ride:} a cycling trip made by a not-registered user.
        \item \textbf{Activity:} a personal record of a registered user's cycling trip, stored by the system to track performance metrics like distance and speed.
        \item \textbf{Publishable Information:} data about a bike path (e.g., status, obstacles) that a registered user has either entered
        making it available to the wider community.
        \item \textbf{Path Score:} a metric computed by BBP to rank route options. It is based on the status of the path and 
        its effectiveness in getting the user from their origin to their destination.   
        \item \textbf{Obstacle:} any significant element or condition on a cycle path that may represent a danger or hindrance to the cyclist (e.g. pothole).
    \end{itemize}

    \subsubsection{Acronyms}
    \begin{itemize}
        \item \textbf{BBP:} Best Bike Paths.           
        \item \textbf{GPS:} Global Positioning System.
        \item \textbf{API:} Application Programming Interface.
    \end{itemize}

    \subsubsection{Abbreviations}
    \begin{itemize}
        \item \textbf{G*:} Goal.
        \item \textbf{WP*:} World Phenomenon.
        \item \textbf{SP*:} Shared Phenomenon.
        \item \textbf{R*:} Requirement.
        \item \textbf{UC*:} Use Case.
        \item \textbf{D*:} Domain Assumption.
    \end{itemize}
    Note: asterisks are intended as a replacement for the number.
        
\subsection{Revision history}
    \begin{itemize}
        \item \textbf{Version 1.0 (23/12/2025)}
        \item \textbf{Vesrion 2.0 (10/01/2026)}: modified Use Case Diagram (Section 3.2.1), Sequence Diagrams 1,2,3,4,58,9,13 (Section 3.2.2) and Functional Requirement 
        RE7 (Section 3.2) after further definitions of those in the DD document.
    \end{itemize}

    \subsection{Reference documents}
    This document is based on the following materials:
    \begin{itemize}
        \item The specification of the RASD and DD assignment of the Software Engineering II course a.y. 2025/26.
        \item Course slides shared on WeBeep.
        \item Past Requirement Analysis and Specification Documents.
    \end{itemize}

\subsection{Document structure}
    \begin{enumerate}
        \item \textbf{Introduction:} a brief description of the project. It contains the main goals and objectives that the final system wants to achieve.
        \item \textbf{Overall description:} this section is a high-level representation of the system and of the interactions of the system with the other actors.
        \item \textbf{Specific requirements:} a detailed list of all the requirements needed for the system to achieve the goals. It contains valuable information for developers.
        \item \textbf{Formal analysis using Alloy:} a formal description of the model of the system with Alloy.
        \item \textbf{Effort spent:} the time spent on each section of the document, for each member of the group.
        \item \textbf{References:} reference to documents or tools used for writing this document.
    \end{enumerate}