\subsection{Purpose}
The growing interest in cycling, whether as a recreational activity, a means of transportation, or a sport, brings with it a significant challenge: 
finding routes that are not only efficient, but also safe and well-maintained. Cyclists often lack reliable and up-to-date information on trail conditions, 
such as the presence of potholes, obstacles, or roads with little traffic. At the same time, many cyclists meticulously log their trips to monitor their performance, 
collecting valuable data that, however, remains siloed. This creates a gap where vital community knowledge about trail quality is not easily shared or accessible.
"Best Bike Paths" (BBP) aims to provide a solution. Commissioned by a cyclists' association, BBP will be a software system designed to create and manage a 
community-driven inventory of cycling routes. The platform will help bridge this information gap by allowing registered users to track their trips while 
simultaneously submitting detailed information on the condition of their routes. Other users, registered or not, will then be able to use this collective data 
to find and display the best possible cycling routes between two points, ranked by a quality score.

\subsubsection{Goals}
\begin{itemize}
    \item \textbf{G1:} A registered user wants to track their personal cycling activities and related performance statistics.
    \item \textbf{G2:} A registered user wants to contribute to the community inventory by sharing reliable information on the condition of the trails (e.g. quality, obstacles, potholes).
    \item \textbf{G3:} Any user (registered or not) wants to find and view the best cycling route between an origin and a destination, based on up-to-date and relevant data.
    \item \textbf{G4:} The cycling association aims to provide the community with a tool to create, consult, and maintain a reliable and centralized inventory of cycling routes.
\end{itemize}