\subsection{Assumptions, dependecies and constraints}
    \subsubsection{Domain Assumptions}
    The following assumptions describe real-world conditions that the system considers true and necessary for the correct functioning of the 
    intended features:

    \begin{itemize} %ci vengono in mente altri domain assumptions??? sei d'accordo con quelli che ho appena elencato?            
        
        \item \textbf{D1 - Hardware Equipment:} It is assumed that the user's mobile device is equipped with functioning and calibrated hardware, 
        specifically: GPS receiver, accelerometer, and gyroscope.
        
        \item \textbf{D2 - Accuracy of user registration data:} It is assumed that the information entered by users during registration phase is correct and truthful.
        
        \item \textbf{D3 - Accuracy of route feedbacks:} It is assumed that the user's feedbacks about routes problems (either manual or automatically detected) are correct and truthful.
        
        \item \textbf{D4 - Accuracy of Basemaps:} It is assumed that third-party mapping services provide a correct topological representation of 
        reality, that is if a road exists on the map then it's assumed that physically exists and that it'is drivable safely by bycicles (unless otherwise reported on BBP).
        
        % Is this assumption included within the first one?
        \item \textbf{D5 - GPS Signal Availability:} It is assumed that, for most of the duration of an outdoor trip, satellite coverage is 
        sufficient to ensure useful location accuracy.
        
        \item \textbf{D6 - Distinguishable Movement Patterns:} It is assumed that the physical characteristics of cycling are sufficiently 
        distinct from those of other modes of transport or walking in order to allow classification algorithms to operate with an acceptable level of 
        accuracy.
    \end{itemize}

    \subsubsection{System Dependencies}
    The BBP system is not an island; it relies on external services to provide added value. Failure of these services degrades the system's 
    functionality as follows:

    \begin{itemize}
        \item \textbf{External Weather Service:} BBP depends on third-party APIs to retrieve weather data (temperature, wind). If this service is 
        unavailable, the system will continue to record trips, but the "Weather Enrichment" feature will not be performed, and the trips will be 
        saved without this metadata.

        \item \textbf{External Mapping Services:} Route visualization and address geocoding depend on external map providers. If these are unavailable, the 
        "Route Search" and "Trip Recording" features will be compromised.
    \end{itemize}

    \subsubsection{System Constraints}      
    \begin{itemize}
        \item \textbf{GDPR and Privacy:} Since the system tracks users' physical movements (sensitive data), the management, storage, and sharing 
        of GPS data must strictly comply with the GDPR regulation. Personal travel data must not be accessible to other users.

        \item \textbf{Energy Consumption:} The automatic detection algorithm must be optimized to avoid draining the mobile device's battery 
        quickly, ensuring coverage of medium-duration trips (e.g., 2-3 hours).

        \item \textbf{Intermittent Connectivity:} Since cycling routes can pass through areas with poor network coverage, the mobile application 
        must be able to store sensor data locally and synchronize it with the server as soon as the connection is re-established.
    \end{itemize}
