\subsection{Functional requirements}
    \paragraph{Authentication and Account Management}
    \begin{itemize}
        \item \textbf{[R1]} The system shall allow any user to create an account.
        \item \textbf{[R2]} The system shall allow registered user to log in using their credentials.
        \item \textbf{[R3]} the system shall allow registered user to reset their account password
        \item \textbf{[R4]} The system shall allow registered user to update their personal profile information.
        \item \textbf{[R5]} The system shall allow registered user to delete their account.
    \end{itemize}

    \paragraph{Trip Recording and Monitoring}
    \begin{itemize}
        \item \textbf{[R6]} The system shall allow registered user to start the recording of a new activity.
        \item \textbf{[R7]} The system shall allow registered user to pause and resume the recording of an active activity.
        
% we've never mentioned to save a trip, up to now once the user stops the trip it' automatically saved, I think we should delete it        
%        \item \textbf{[R7]} The system shall allow registered user to save a trip.

        \item \textbf{[R8]} During the recording, the system shall track the user's position and its performance statistics.
        \item \textbf{[R9]} Upon completion of a trip, the system shall automatically retrieve weather data from an external service, 
        if available, and associate it to the saved activity.
    \end{itemize}

    \paragraph{Data Contribution and Governance}
    \begin{itemize}
        \item \textbf{[R10]} The system shall allow registered user to insert manual reports regarding the status of a path.
        \item \textbf{[R11]} The system shall allow registered user to submit feedback regarding the Path Status.
        \item \textbf{[R12]} The system shall allow registered user to insert manual reports regarding problems on the path.
        \item \textbf{[R13]} The system shall allow registered user to enable automatic detection during an activity.
        \item \textbf{[R14]} When automatic detection is active, the system shall analyze data from the device's sensors to detect potential anomalies.
        \item \textbf{[R15]} The system shall present the list of automatically detected anomalies to the registered user at the end of the recorded 
        activity for review.
        \item \textbf{[R16]} The system shall allow the registered user to confirm or discard a detected anomaly.
    \end{itemize}

    \paragraph{Path Planning and Visualization}
    \begin{itemize}
        \item \textbf{[R17]} The system shall compute valid cycling routes between a specified starting point and a destination based on the 
        available physical road network. 
        \item \textbf{[R18]} The system shall compute and visualize one or more valid routes between the specified points on a map.
        \item \textbf{[R19]} The system shall compute a Path Score for each route derived from available inventory data
        \item \textbf{[R20]} The system shall display confirmed obstacles on the map with visual markers.
        \item \textbf{[R21]} The system shall allow the user to filter the search on Path properties. 
    \end{itemize}

    \paragraph{Trip History}
    \begin{itemize}
        \item \textbf{[R22]} The system shall allow registered user to view the list of its past activities.
        \item \textbf{[R23]} The system shall allow registered user to view the details of a specific past trip, including the route on 
        the map, statistics, and weather data (if they exist).
        \item \textbf{[R24]} The system shall allow registered users to delete a specific activity from their history.
        \item \textbf{[R25]} The system shall allow the user to search a specific activity in its history.
        \item \textbf{[R26]} The system shall allow the user to filter the view of its history.
    \end{itemize}

