\section{Specific requirements}
\input{RASD/Section3/external_interface_requirements.tex}    
\input{RASD/Section3/functional_requirements.tex}
\input{RASD/Section3/use_case.tex}
\input{RASD/Section3/requirement_mapping.tex}

% ------------------------------------------------------------------------------------------------------------------
\subsection{Performance requirements}
    Given the nature of BBP as a mobile application that also operates in active mobility contexts, performance is critical not only for the user
        experience, but also for the security and reliability of the collected data.

    \begin{itemize}
        \item \textbf{Interface Responsiveness:} The system must ensure immediate response times for critical interactions during cycling, with a 
        latency of less than 200 ms, to avoid dangerous distractions for the user.

        \item \textbf{Real-Time Data Processing:} During "Automatic Detection" mode, the local algorithm on the device must process sensor data in 
        real time.

        \item \textbf{Routing:} The route search functionality must return results, complete with \textit{Path Score}, within 3 seconds for 
        requests in a standard urban environment (10 km radius), ensuring smooth planning.

        \item \textbf{Backend Scalability:} The system must be able to handle simultaneous load peaks (e.g., weekends or cycling events), scaling 
        horizontally to support thousands of simultaneous trip uploads without data loss.

        % I think we could trim out this part, it's already tackled leter in the document
        %\item \textbf{Reliability:} The backend service must guarantee 99.9\% uptime on a monthly basis, ensuring that users can 
        %always sync their trips and access maps.
    \end{itemize}
    \pagebreak

% ------------------------------------------------------------------------------------------------------------------
\subsection{Design Constraints}

    \subsubsection{Standards Compliance}
    The BBP system adheres to rigorous international standards to ensure interoperability, security, and regulatory compliance.

    \begin{table}[H]
        \centering
        \renewcommand{\arraystretch}{1.3}
        \begin{tabular}{|l|p{0.7\textwidth}|}
            \hline
            \textbf{Standard} & \textbf{Description} \\
            \hline
            \textbf{GDPR (EU 2016/679)} & The system manages sensitive geolocation and user profiling data. All processing must comply with the 
            General Data Protection Regulation, guaranteeing the right to be forgotten and data minimization. \\
            \hline
            \textbf{WGS 84} & Geodetic reference standard for the GPS system. All stored and exchanged coordinates must comply with this standard 
            to ensure compatibility with global maps. \\
            \hline
%   also here I would probably remove this part (where was mentioned to gave interoperability with other sport services)
%            \textbf{GPX (GPS Exchange)} & The system should support the export of trip data in the standard XML format for GPS data, facilitating 
%            interoperability with other sports platforms. \\
%            \hline
            \textbf{ISO/IEC 27001} & Standard for information security management, applied to protect the backend infrastructure and user data 
            from unauthorized access. \\
            \hline
        \end{tabular}
        \caption{Compliance standards adopted by BBP}
        \label{tab:standards}
    \end{table}

    \subsubsection{Hardware Limitations}
    The mobile application must operate in a resource-constrained environment, typical of mobile devices during extended outdoor use.

    \begin{itemize}
        \item \textbf{Power Consumption:} The automatic detection algorithm (GPS + Sensors) must be optimized to consume no more than 10-15\% 
        battery power per hour of use on an average device, ensuring the user does not run out of battery power while traveling.
        \item \textbf{Required Sensors:} Full use of the app is contingent on the physical presence of a calibrated accelerometer and gyroscope. 
        Older or low-end devices without these sensors will only be able to use the app in limited mode (without automatic detection).
        \item \textbf{Intermittent Connectivity:} The design must include an "offline-first" mode for data recording. Upload to the server must 
        occur asynchronously when the connection is stable, handling any timeouts without losing local data.
    \end{itemize}

    \subsubsection{Any Other Constraint}
    \begin{itemize}
        \item \textbf{GPS Accuracy:} The accuracy of obstacle detection is limited by the accuracy of the device's civilian GPS. The system must 
        include clustering or manual correction mechanisms to handle inherent hardware inaccuracy.
        \item \textbf{Operating System:} The application must be compatible with Android and iOS versions released in the last 3 years to ensure 
        access to the latest APIs for efficient background sensor management.
        \item \textbf{Local Data Processing:} To ensure responsiveness and minimize mobile data usage, the raw processing of high-frequency sensor 
        data must be performed locally on the user's device. The system is constrained to transmit only the identified "candidate anomalies" to 
        the server, rather than the continuous raw data stream.
    \end{itemize}

\input{RASD/Section3/system_attributes.tex}

